### 2013-10-16 chi2014/qualitative.tex

Another type of riffing is \emph{repeat riffing}. Under this strategy, a participant produces multiple responses with only slight differences between them. For example (PXXX):

\begin{itemize}
    \item recycle to make better MP3/iPod players
    \item use the circuits to for the iPod/MP3 to power other things that are more recent
\end{itemize}

In this case, the participant is providing the same idea (namely, creating new electronic devices from the parts) twice.

@@

\begin{itemize}
    \item Jukebox music selector in bars
    \item Commercials in bar bathrooms (hold the bar element)
    \item Tapper handles for beer (hold the alcohol element)
\end{itemize}

Hold riffing can also involve holding language terms constant even when the meaning of the term changes between responses, as in free association. For example (PXXX):

\begin{itemize}
    \item beer coaster
    \item drink coaster (generalization riffing)
    \item roller coaster (hold riffing)
\end{itemize}

\emph{Continuation riffing} is the strategy of creating another idea that assumes the previous idea has already been implemented. The new idea on the implications or consequences of the previous. For example (PXXX):

@@

\subsubsection{Language use}

Some participants re-use sentence structure or phrasings across multiple responses. We call this strategy \emph{language repetition}. For example (PXXX):

In this example, while language is re-used, each instance is also a new idea unrelated to the previous.
However, language repetition is especially common in repeat riffing, as this example (PXXX) shows:

\begin{itemize}
    \item wrap yarn around it
    \item wrap twine around it
    \item wrap string around it
\end{itemize}

@@

Under this category of strategies, responses provide some elements of a solution to the problem, but further idea generation is required to implement the solution. Some responses provide a reduced scope, but do not explore within that scope. Others would provide a goal for a solution to obtain but not provide a plan for achieving that goal. Finally, some responses passed the problem to a third party.

@@

In some responses, an end goal has been established, but any implementation of the goal requires further idea generation. We call this strategy \emph{goal without plan}. For example, a selection of responses from PXXX:

In this case, the goal of creating a new electronic device is given, but it is not clear what will be created or how the materials will be re-used.

>>>>

Another type of riffing is \emph{repeat riffing}. Under this strategy, a participant produces multiple responses with only slight differences between them, such that the group of ideas could be easily summarized as one idea without significant loss of information. For example (PXXX):

\begin{itemize}
    \item extract usage data
    \item extract texts
    \item extract gps data
\end{itemize}

In this case, all three ideas could be summarized with "extract the data on the device".

@@

\begin{itemize}
    \item Jukebox music selector in bars
    \item Commercials in bar bathrooms 
    \item Tapper handles for beer 
\end{itemize}

In this example, the setting of the application is held constant across riffs: a bar.

Another realization of hold riffing holds language term constant between unrelated ideas. For example (PXXX):

\emph{Continuation riffing} is the strategy of creating another idea that relies on the implications or consequences of a previous idea. The new idea cannot be understood without the context of the previous. For example (PXXX):

@@

@@

Under this category of strategies, responses provide some elements of a solution to the problem, but further idea generation is required to implement the solution. The following ideas (PXXX) are all examples of partial solutions:

In these responses, there is a clear recommendation that we recycle components of the MP3 player to produce new electronics, but it is unclear what we would make or how we would use the parts. Essentially, we are left with new brainstorming problems to solve.

As with riffing and problem scoping, there are four sub-strategies of partial solutions: problem scoping without solution, goal without plan, plan without goal, and passing the problem.

@@

In some responses, an end goal has been established, but any implementation of the goal requires further idea generation. We call this strategy \emph{goal without plan}. The list of responses at the beginning of this section are examples of the goal without plan strategy.
The goal of creating a new electronic device is given, but it is not clear what will be created or how the materials will be re-used.
